---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "60%",
  out.height = "60%"
)
```

# wordplay

<!-- badges: start -->
[![R-CMD-check](https://github.com/hlan22/wordplay/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hlan22/wordplay/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/hlan22/wordplay/graph/badge.svg)](https://app.codecov.io/gh/hlan22/wordplay)
[![pkgdown](https://github.com/hlan22/wordplay/actions/workflows/pkgdown.yaml/badge.svg)](https://hlan22.github.io/wordplay/)

[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![License: CC0](https://img.shields.io/badge/License-CC0-lightgrey.svg)](https://creativecommons.org/publicdomain/zero/1.0/)
[![R version](https://img.shields.io/badge/R-%3E%3D4.0.0-blue)](https://github.com/hlan22/wordplay/blob/main/DESCRIPTION)
[![Dev version](https://img.shields.io/badge/dev%20version-1.0.0-brightgreen)](https://github.com/hlan22/wordplay)
[![CRAN status](https://www.r-pkg.org/badges/version/wordplay)](https://CRAN.R-project.org/package=wordplay)
<!-- badges: end -->

The aim of `wordplay` is to learn more about your favorite list of words! 
Learn about metrics such as length, frequent starting letters, and much more with ease!

#### Table of Contents

* [Installation](#installation)
* [Functions](#functions)
* [Dependencies](#dependencies)
* [Example Use](#example-use)
* [Code of Conduct](#code-of-conduct)
* [Licenses](#licenses)

## Installation

You can install the development version of `wordplay` from [GitHub](https://github.com/) with:

``` r
install.packages("pak")

pak::pak("hlan22/wordplay")
```

## Functions

* `all_words_summary`
* `word_characteristics`
* `word_length_plot`
* `top_words_plot`

## Dependencies

The following R packages are used by this package:

* `dplyr`: 1.1.4
* `forcats`: 1.0.0
* `ggplot2`: 3.5.1
* `stats`: 4.4.1
* `stringr`: 1.5.1
* `stringi`: 1.8.4
* `tibble`: 3.2.1
* `testthat`: 3.2.1

## Example Use

This is a basic example which shows you how to solve a common problem:

```{r example}

library(wordplay)

# use example list of words, such as the greek alphabet
greek_alphabet <- data.frame(
  word = c(
    "Alpha", "Beta", "Gamma", "Delta", "Epsilon", "Zeta", "Eta", "Theta",
    "Iota", "Kappa", "Lambda", "Mu", "Nu", "Xi", "Omicron", "Pi", "Rho",
    "Sigma", "Tau", "Upsilon", "Phi", "Chi", "Psi", "Omega"
  ))

# learn about size of list and length of the words overall
all_words_summary(greek_alphabet)

# learn about individual words themselves in a table
summary(word_characteristics(greek_alphabet))

# visualize the different lengths of words in the list
word_length_plot(greek_alphabet)

# learn if there are repeating words in the list; not applicable to this example
top_words_plot(greek_alphabet)
```


## Code of Conduct

Please note that `wordplay` is released with a [Code of Conduct](https://hlan22.github.io/wordplay/CODE_OF_CONDUCT.md). 
By contributing to this project, you agree to abide by its terms.

## Licenses

This project is dual-licensed under the following:

- **[Creative Commons Zero v1.0 Universal (CC0 1.0)](https://creativecommons.org/publicdomain/zero/1.0/)** You can copy, modify, distribute and perform the work, even for commercial purposes, all without asking permission.

- **[MIT License](LICENSE-MIT.md)** A short and permissive software license. You can use it in proprietary software provided that all copies include the license terms and the copyright notice.
  
